\TITLE

### 2024-08-08 paper/main.tex
add paragraph on public vs permissioned blockchains

>>>>

The choice between permissioned and permissionless blockchain touches on an ideological dispute about freedom and trust. The use of permissioned blockchain is recommended in domain-specific applications, such as closed consortia between distrustful parties. All the referenced protocols we've found use a public blockchain, suggesting that the fair exchange problem is allegedly not one of them. The public blockchain offers the irreplaceable qualities of total decentralisation, transparency, openness, no infrastructure maintenance costs (only transaction costs) and a different but arguably higher level of security (for networks with a high number of validators). In addition, protocols designed for public blockchains have a higher degree of generality and can be implemented in any private or permissioned blockchain. Therefore, for the rest of the paper, we only consider public networks.
